\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE Alex Morgan}\\
  Chicago, IL \quad | \quad alex.morgan@example.com \quad | \quad
  https://scholar.google.com/citations?user=alex-morgan-materials
\end{center}

\section*{Summary}
Scientific ML scientist for molecular simulation and materials discovery, with experience in
active learning, machine learning potentials, and production-grade HPC workflows.

\section*{Selected Experience}
\textbf{Frontier Materials AI} \hfill 2023--Present\\
Scientific ML Scientist
\begin{itemize}
  \item Built \underline{scientific machine learning} workflows for molecular dynamics, surrogate modeling, and experiment selection.
  \item Trained machine learning potentials and graph neural networks with PyTorch for materials screening.
  \item Deployed LAMMPS, PLUMED, and Bayesian optimization loops on GPU-enabled clusters.
\end{itemize}

\textbf{Bay City Computing} \hfill 2020--2023\\
Simulation Scientist
\begin{itemize}
  \item Connected high-throughput simulation outputs with feature stores and decision dashboards for research teams.
  \item Built data pipelines for model retraining, uncertainty tracking, and performance review across campaigns.
  \item Bridged molecular modeling, materials informatics, and HPC operations in cross-functional projects.
\end{itemize}

\section*{Selected Publications}
\begin{itemize}
  \item Morgan, A.; Zhao, Y. ``Closed-loop simulation and active learning for soft-material discovery.'' \textit{npj Comput. Mater.} (accepted)
  \item Morgan, A.; Patel, R.; Gomez, I. ``Uncertainty-aware machine learning potentials for molecular assembly.'' \textit{J. Chem. Phys.} (under revision)
\end{itemize}

\end{document}
