\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE Alex Morgan}\\
  Chicago, IL \quad | \quad alex.morgan@example.com \quad | \quad
  https://scholar.google.com/citations?user=alex-morgan-protein
\end{center}

\section*{Summary}
Computational scientist for protein modeling, coarse-grained simulation, and scientific machine learning
across peptide assembly, biomolecular condensates, and sequence-to-ensemble problems.

\section*{Selected Experience}
\textbf{Protein Systems Lab} \hfill 2023--Present\\
Computational Biologist
\begin{itemize}
  \item Developed \underline{protein modeling} workflows for intrinsically disordered proteins and condensate-forming systems.
  \item Combined coarse-grained molecular dynamics with scientific machine learning for ensemble prediction.
  \item Built analysis tooling for sequence-conditioned simulation studies and experiment comparison.
\end{itemize}

\textbf{Sequence Design Studio} \hfill 2020--2023\\
Research Scientist
\begin{itemize}
  \item Linked protein design screens with simulation-guided feature engineering and ranking models.
  \item Ran scalable Python workflows for biomolecular condensates, peptide assembly, and mutational scanning.
  \item Partnered with wet-lab collaborators on interpretable modeling and candidate prioritization.
\end{itemize}

\section*{Selected Publications}
\begin{itemize}
  \item Morgan, A.; Rivera, D. ``Sequence-aware coarse-grained modeling of disordered protein assembly.'' \textit{Biophys. J.} (accepted)
  \item Morgan, A.; Huang, K. ``Experiment-aware generative modeling for protein ensembles.'' \textit{bioRxiv} (preprint)
\end{itemize}

\end{document}
