\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE Alex Morgan}\\
  Chicago, IL \quad | \quad alex.morgan@example.com \quad | \quad
  https://scholar.google.com/citations?user=alex-morgan-general
\end{center}

\section*{Summary}
Simulation-first computational scientist bridging computational chemistry, molecular simulation,
materials informatics, and scientific machine learning for molecules and soft materials.

\section*{Selected Experience}
\textbf{North Ridge Discovery} \hfill 2023--Present\\
Computational Scientist
\begin{itemize}
  \item Led \underline{molecular dynamics} and enhanced sampling studies for solution-phase self-assembly and crystallization.
  \item Built PyTorch and graph neural network workflows for structure-property prediction and active learning.
  \item Maintained production LAMMPS, PLUMED, CP2K, and ORCA workflows on shared HPC clusters.
\end{itemize}

\textbf{Lakefront Materials Lab} \hfill 2020--2023\\
Research Scientist
\begin{itemize}
  \item Combined DFT, coarse-grained simulation, and Bayesian optimization for molecular design decisions.
  \item Connected experimental screening data with scientific machine learning models for materials selection.
  \item Authored reproducible analysis pipelines spanning Python, Jupyter, and cloud/HPC execution.
\end{itemize}

\section*{Selected Publications}
\begin{itemize}
  \item Morgan, A.; Patel, R.; Lee, S. ``Physics-guided active learning for crystallization pathways.'' \textit{J. Chem. Theory Comput.} (accepted)
  \item Morgan, A.; Rivera, D.; Chen, L. ``Closed-loop molecular simulation for self-assembling materials.'' \textit{Chem. Sci.} (advance article)
  \item Morgan, A.; Huang, K. ``Experiment-aware coarse-grained models for peptide assembly.'' \textit{Macromolecules} (under revision)
\end{itemize}

\end{document}
