\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE Alex Morgan}\\
  Chicago, IL \quad | \quad alex.morgan@example.com \quad | \quad
  https://scholar.google.com/citations?user=alex-morgan-compchem
\end{center}

\section*{Summary}
Computational chemistry scientist specializing in molecular modeling, free-energy methods,
force-field development, and simulation-guided decisions for small molecules and soft materials.

\section*{Selected Experience}
\textbf{Catalyst Forge} \hfill 2023--Present\\
Computational Chemist
\begin{itemize}
  \item Built \underline{computational chemistry} workflows using DFT, ORCA, CP2K, and molecular dynamics.
  \item Developed force-field and free-energy pipelines for molecular recognition, polymorph ranking, and formulation design.
  \item Partnered with experimental teams to prioritize chemistry through interpretable simulation readouts.
\end{itemize}

\textbf{MolDesign Systems} \hfill 2020--2023\\
Scientist, Molecular Modeling
\begin{itemize}
  \item Applied enhanced sampling, cheminformatics, and Bayesian optimization to accelerate lead triage.
  \item Integrated PyTorch models with molecular simulation to improve campaign selection under sparse data.
  \item Maintained reproducible Python tooling for analysis, report generation, and hypothesis tracking.
\end{itemize}

\section*{Selected Publications}
\begin{itemize}
  \item Morgan, A.; Patel, R. ``Transferable free-energy workflows for crystal engineering.'' \textit{J. Phys. Chem. B} (accepted)
  \item Morgan, A.; Singh, T. ``Machine learning potentials for solvent-mediated molecular assembly.'' \textit{J. Chem. Inf. Model.} (under revision)
\end{itemize}

\end{document}
