\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE Taylor Brooks}\\
  Chicago, IL \quad | \quad taylor.brooks@example.com \quad | \quad
  https://www.linkedin.com/in/taylor-brooks-demo
\end{center}

\section*{Summary}
Commercial operator combining account growth, revenue programs, enablement, and
cross-functional execution for SaaS sales organizations.

\section*{Selected Experience}
\textbf{Atlas Revenue Systems} \hfill 2023--Present\\
Account Growth Manager
\begin{itemize}
  \item Led \underline{expansion planning} for strategic accounts by pairing usage data, success plans, and executive mapping.
  \item Built renewal and upsell briefs that improved forecast clarity for account executives and leadership.
  \item Coordinated customer stories, objection handling, and ROI framing for enterprise deal cycles.
\end{itemize}

\textbf{Northstar Revenue Cloud} \hfill 2020--2023\\
Revenue Programs Manager
\begin{itemize}
  \item Supported pipeline generation programs with campaign follow-up, SDR enablement, and stage-conversion dashboards.
  \item Standardized handoff processes between marketing, SDRs, AEs, and customer success during growth sprints.
  \item Built reporting packages for bookings, win-loss themes, reference usage, and expansion readiness.
\end{itemize}

\section*{Selected Wins}
\begin{itemize}
  \item Helped enterprise teams expand multi-product ARR by \$900K through usage-based account planning.
  \item Improved stage-to-stage visibility with shared dashboards used in weekly pipeline and renewal reviews.
  \item Built repeatable reference and case-study workflows for executive sponsor meetings and late-stage deals.
\end{itemize}

\end{document}
