\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE Taylor Brooks}\\
  Chicago, IL \quad | \quad taylor.brooks@example.com \quad | \quad
  https://www.linkedin.com/in/taylor-brooks-demo
\end{center}

\section*{Summary}
Revenue-minded go-to-market operator blending growth marketing, lifecycle automation,
customer success, and account expansion for B2B SaaS teams.

\section*{Selected Experience}
\textbf{Northstar Revenue Cloud} \hfill 2023--Present\\
Growth \& Lifecycle Manager
\begin{itemize}
  \item Built \underline{lifecycle automation} in HubSpot and Salesforce, lifting MQL-to-SQL conversion by 28\%.
  \item Launched webinar, email, and paid social plays that influenced \$2.4M in qualified pipeline.
  \item Created weekly reporting cadences for CAC, funnel conversion, and handoff quality across marketing and sales.
\end{itemize}

\textbf{BrightPath Software} \hfill 2020--2023\\
Customer Success \& Expansion Lead
\begin{itemize}
  \item Standardized onboarding playbooks that cut time-to-value by 22\% for mid-market customers.
  \item Ran renewal risk reviews and save plans across at-risk accounts, protecting \$1.4M ARR.
  \item Turned customer wins into case studies, references, and expansion plays with sales and product teams.
\end{itemize}

\section*{Selected Wins}
\begin{itemize}
  \item Built a 14-account customer reference bench for late-stage sales cycles and analyst calls.
  \item Reduced first-response time by 31\% after redesigning support routing, macros, and knowledge-base content.
  \item Partnered with RevOps to unify campaign, adoption, and expansion reporting for weekly exec reviews.
\end{itemize}

\end{document}
