\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE Taylor Brooks}\\
  Chicago, IL \quad | \quad taylor.brooks@example.com \quad | \quad
  https://www.linkedin.com/in/taylor-brooks-demo
\end{center}

\section*{Summary}
Customer success leader focused on onboarding, adoption, renewal health, and
expansion planning for B2B SaaS customer portfolios.

\section*{Selected Experience}
\textbf{BrightPath Software} \hfill 2023--Present\\
Customer Success Manager
\begin{itemize}
  \item Designed \underline{onboarding playbooks} and success-plan templates that cut time-to-value by 22\%.
  \item Built renewal-risk cadences across customer health, executive outreach, and mitigation tracking.
  \item Led quarterly business reviews that translated adoption insights into expansion and advocacy opportunities.
\end{itemize}

\textbf{SignalDesk} \hfill 2020--2023\\
Senior Client Success Specialist
\begin{itemize}
  \item Managed a book of strategic accounts with 96\% gross renewal performance across two fiscal years.
  \item Partnered with support and product teams to reduce repeat tickets and improve knowledge-base coverage.
  \item Converted customer feedback into roadmap themes, enablement material, and rollout checklists.
\end{itemize}

\section*{Selected Wins}
\begin{itemize}
  \item Protected \$1.4M ARR through targeted save plans and multithreaded stakeholder alignment.
  \item Grew customer reference participation from 4 to 14 active advocates in twelve months.
  \item Reduced average escalation response time by 31\% through support workflow redesign.
\end{itemize}

\end{document}
