\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{leftmargin=1.2em,itemsep=0.2em,topsep=0.2em}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE Taylor Brooks}\\
  Chicago, IL \quad | \quad taylor.brooks@example.com \quad | \quad
  https://www.linkedin.com/in/taylor-brooks-demo
\end{center}

\section*{Summary}
Growth marketing leader focused on pipeline generation, lifecycle orchestration,
and conversion analytics for SaaS teams selling into SMB and mid-market accounts.

\section*{Selected Experience}
\textbf{Northstar Revenue Cloud} \hfill 2023--Present\\
Growth Marketing Manager
\begin{itemize}
  \item Rebuilt \underline{demand generation} programs across paid search, webinars, partner campaigns, and nurture tracks.
  \item Increased marketing-sourced SQL volume by 34\% while lowering blended CAC by 17\% over two quarters.
  \item Owned experimentation, audience segmentation, and budget pacing across HubSpot, Salesforce, and LinkedIn Ads.
\end{itemize}

\textbf{PulseLoop SaaS} \hfill 2020--2023\\
Lifecycle Marketing Lead
\begin{itemize}
  \item Built onboarding and expansion journeys that improved product-qualified lead conversion by 21\%.
  \item Partnered with product marketing on content offers, case studies, and demo follow-up programs for ABM targets.
  \item Standardized attribution and funnel reporting for weekly executive reviews and quarterly planning.
\end{itemize}

\section*{Selected Wins}
\begin{itemize}
  \item Influenced \$3.1M in pipeline from integrated paid, webinar, and lifecycle campaigns.
  \item Shipped an always-on customer story program that produced 18 reusable proof points for sales teams.
  \item Created a shared scorecard for MQL quality, speed-to-lead, and channel efficiency across GTM leadership.
\end{itemize}

\end{document}
